\documentclass[a4paper,runningheads]{llncs}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{boxedminipage}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{rotating}
\usepackage{xstring}

\newcommand{\ooo}[1]{\textsf{101#1}}
\newcommand{\oneohone}{\ooo{}}
\newcommand{\MediaWiki}{\textsf{MediaWiki}}
\newcommand{\Wikipedia}{\textsf{Wikipedia}}
\newcommand{\WikipediaUrl}{http://en.wikipedia.org/wiki}
\newcommand{\WikipediaPage}[1]{%
  \protect\StrSubstitute{#1}{ }{_}[\wikiurl]%
  \protect\href{\WikipediaUrl/\wikiurl}{\emph{#1}}}
\newcommand{\WikipediaCategory}[1]{%
  \protect\StrSubstitute{Category:#1}{ }{_}[\wikiurl]%
  \protect\href{\WikipediaUrl/\wikiurl}{\emph{#1}}}
\newcommand{\WikiTaxEmptyCell}{--}
\newcommand{\WikiTax}{\textsf{WikiTax}}
\newcommand{\WikiTaxCategory}[1]{\WikipediaCategory{#1}}
\newcommand{\WikiTaxSubcategory}[1]{\WikipediaCategory{#1}}
\newcommand{\WikiTaxComment}[1]{#1}
\newcommand{\WikiTaxNewLine}{\\\hline}

%\clubpenalty = 10000 
%\widowpenalty = 10000 
%\displaywidowpenalty = 10000

\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily\scriptsize,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}

\author{Ralf L\"ammel \and Dominik Mosen \and Andrei Varanovich}
\institute{University of Koblenz-Landau, Software Languages Team}
%\title{Exploration of Wikipedia's categories for software languages with \WikiTax}
\title{Method and tool support for classifying software languages with \Wikipedia}
%\subtitle{Tool demonstration}

\begin{document}

\maketitle

\begin{abstract} 

  \Wikipedia{} provides useful input for efforts on mining taxonomies
  or ontologies in specific domains. In particular, \Wikipedia's
  categories serve classification. In this paper, we describe a
  method and a corresponding tool, \WikiTax, for exploring
  \Wikipedia's category graph with the objective of supporting the
  development of a classification of software languages. The category
  graph is extracted level by level. The extracted graph is visualized
  in a tree-like manner. Category attributes (i.e., metrics) such as
  depth are visualized. Irrelevant edges and nodes may be
  excluded. These exclusions are documented while using a manageable
  and well-defined set of `exclusion types' as comments.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{intro}
\input{approach}
\input{study}
\input{concl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{splncs03}
\bibliography{paper}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
